Gompertzian growth as infinitely correlated non-local growth

### 2023-08-07 arxiv2/new_draft.tex
rephrase

It is worth noting that the original formulation of the Gompertz model made by Gompertz himself was concerning mortality rates as a function of age. He noticed that mortality rates increased at a geometric rate with age. In this context the ubiquitous stressor postulated above is of course time itself, clearly an external source. In other words, Gompertz growth arises without the need for communication across entities, but is mediated by a mutual field.

>>>>

It is worth noting that the original formulation of the Gompertz model made by Gompertz himself was concerning mortality rates as a function of age. He noticed that mortality rates increased at a geometric rate with age. In this context the ubiquitous stressor postulated above is of course time itself. In other words, Gompertz growth arises without the need for communication across entities, but is mediated by a mutual field. One could then see the entities as communicating indirectly though this field, in a perceived one-way fashion from the field to each entity.
